---
title: "Accelerometer (browser)"
subtitle: "Sampling rate accuracy"
author: "Pedro Neto"
date: "27.01.2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
source('/Users/pdealcan/Documents/github/doc_suomi/code/utils.R')
library(dplyr)
library(rmarkdown)
library(ggplot2)
require(jsonlite)

filepath<-"/Users/pdealcan/Documents/github/doc_suomi/text/CoE/code/trial_data_2.json"
content<-readLines(filepath)
res<-lapply(content,fromJSON)

dt = data.frame(res)

```

# Setup

When the user presses the "Start" button, a song starts playing and accelerometer data starts being collected along axis $x$, $y$ and $z$. Sampling occurs every 60ms, and everytime it occurs, I monitor timing thgough 1) UNIX epoch (ms since 1.1.1970); and 2) amount of time passed in the song. That way I have 2 time-stamps associated with each accelerometer reading.

```{r setup2, include=TRUE}
dt %>%
  melt(id.vars = c("thist", "audiohist")) %>%
  ggplot(aes(x = audiohist, y = value))+
    facet_wrap(~variable)+
    geom_path()+
    ylab("Accelerometer")+
    xlab("Audio timing (s)")
```

# Analyses

Here I analyse the consistency of these readings.


## Difference between time elapsed from audio-time and UNIX epoch

```{r enhanced, echo=TRUE}
time_elapsed = max(dt$thist) - min(dt$thist) #time elapsed from UNIX epochs 
time_elapsed - ((max(dt$audiohist) - min(dt$audiohist))*1000)
```

## Sampling rate (difference between ideal and observed)
```{r enhanced2, echo=TRUE}
sampling_frequency = 60
expected_sr = 1000/sampling_frequency
actual_sr = (1000*length(dt$thist))/time_elapsed

expected_sr - actual_sr
```

```{r enhanced3, echo=FALSE}
difs = c()
for(i in 1:(length(dt$thist)-1)){
  difs = c(difs, dt$thist[i+1] - dt$thist[i])
}
```

## Consistency of inter-sampling intervals

Here I calculated the amount of time passed between samples $n$ and $n+1$ (difs).

```{r enhanced4, echo=TRUE}
sum(difs) == time_elapsed
```
## Mean time (ms) between samples (Expected was 60)
```{r enhanced5, echo=TRUE}
mean(difs) 
```
## Dispersion measures
```{r enhanced6, echo=TRUE}
sd(difs)
max(difs)
min(difs)
```

